% ОБЯЗАТЕЛЬНО ИМЕННО ТАКОЙ documentclass!
% (Основной кегль = 14pt, поэтому необходим extsizes)
% Формат, разумеется, А4
% article потому что стандарт не подразумевает разделов
% Глава = section, Параграф = subsection
% (понятия "глава" и "параграф" из стандарта)
\documentclass[a4paper,article,14pt]{extarticle}

% Подключаем главный пакет со всем необходимым
\usepackage{spbudiploma}

% Пакеты по желанию (самые распространенные)
% Хитрые мат. символы
\usepackage{euscript}
% Таблицы
\usepackage{longtable}
\usepackage{makecell}
% Картинки (можно встявлять даже pdf)
\usepackage[pdftex]{graphicx}

\usepackage{amsthm,amssymb, amsmath}
\usepackage{textcomp}


\begin{document}

% Титульник в файле titlepage.tex
\input{titlepage.tex}

% Содержание
\tableofcontents
\pagebreak

\input{introduction.tex}
\pagebreak

\input{problem_statement.tex}
\pagebreak

\input{research.tex}
\pagebreak

\input{part1.tex}
\pagebreak

\input{part2.tex}
\pagebreak

\input{part3.tex}
\pagebreak

\input{conclusion.tex}

\pagebreak

% Библиография в cpsconf стиле
% Аргумент {1} ниже включает переопределенный стиль с выравниванием слева
\begin{thebibliography}{1}
\bibitem{bib1} Robin Burke \flqq Multisided Fairness for Recommendation\frqq. Presented as a poster at the 2017 Workshop on Fairness, Accountability, and Transparency in Machine Learning (FAT/ML 2017), \href{https://arxiv.org/pdf/1707.00093.pdf}{arxiv.org/pdf/1707.00093.pdf}.
\bibitem{bib2} Alexandra Chouldechova \flqq Fair prediction with disparate impact: A study of bias in recidivism prediction instruments\frqq. FATML 2016 conference paper. A long version of the paper available on the author's website, \href{https://arxiv.org/pdf/1610.07524.pdf}{arxiv.org/pdf/1610.07524.pdf}.
\bibitem{bib3} Mesut Kaya, Derek Bridge \flqq Accurate and Diverse Recommendations Using Item-Based SubProfiles\frqq. 	hirty-First International Florida Artificial Intelligence Research Society Conference, 2018, pp. 462--467 \href{https://www.insight-centre.org/sites/default/files/publications/kaya-bridge-2017.pdf}{www.insight-centre.org/sites/default/files/publications/kaya-bridge-2017.pdf}.
\bibitem{bib4} Harald Steck \flqq Calibrated Recommendations\frqq. RecSys '18: Proceedings of the 12th ACM Conference on Recommender Systems, 2018, pp. 154--162, \href{https://doi.org/10.1145/3240323.3240372}{doi.org/10.1145/3240323.3240372}.
\bibitem{bib5} Van Dang and W. Bruce Croft \flqq Diversity by Proportionality: An Election-based Approach to Search Result Diversification\frqq. SIGIR '12: Proceedings of the 35th international ACM SIGIR conference on Research and development in information retrieval, 2012, pp. 65--74, \href{https://doi.org/10.1145/2348283.2348296}{doi.org/10.1145/2348283.2348296}.
\bibitem{bib6} David M W Powers \flqq Evaluation: From Precision, Recall and F-Factor to ROC, Informedness, Markedness and Correlation\frqq. Journal of Machine Learning Technologies, 2011, pp. 37--63, \href{https://csem.flinders.edu.au/research/techreps/SIE07001.pdf}{csem.flinders.edu.au/research/techreps/SIE07001.pdf}.
\bibitem{bib7} Кендалл М., Стьюарт А. \flqq Статистические выводы и связи\frqq. Наука, 1973.
\bibitem{ig2vec} Ivan Medvedev, Haotian Wu, Taylor Gordon \flqq Powered by AI: Instagram’s Explore recommender system\frqq. Facebook Artificial Intelligence, 2019.
\bibitem{sur} Nicolas Hug \flqq Surprise a Python library for recommender systems\frqq, 2017. \href{http://surpriselib.com}{surpriselib.com}.
\bibitem{SciKits} Официальный сайт документации SciKits: \href{https://www.scipy.org/scikits.html}{www.scipy.org/scikits.html}.
\bibitem{Scipy} Pauli Virtanen, Ralf Gommers, Travis E. Oliphant,
Matt Haberland, Tyler Reddy, David Cournapeau, Evgeni Burovski,
Pearu Peterson, Warren Weckesser, Jonathan Bright, St{\'e}fan J. van der Walt,
Matthew Brett, Joshua Wilson,  Jarrod K. Millman, Nikolay Mayorov, 
Andrew Nelson, Eric Jones, Robert Kern,  Eric Larson,
CJ Carey, {\.I}lhan Polat,  Yu {Feng},  Eric W. {Moore},
Jake {Vand erPlas},  Denis {Laxalde},  Josef
{Perktold},  Robert {Cimrman},  Ian {Henriksen},  E.~A.
{Quintero},  Charles R {Harris},  Anne M. {Archibald}, 
Ant{\^o}nio H. {Ribeiro},  Fabian {Pedregosa},  Paul
{van Mulbregt} \flqq SciPy 1.0: Fundamental Algorithms for Scientific
Computing in Python\frqq. Nature Methods 2020, \href{https://doi.org/10.1038/s41592-019-0686-2}{doi.org/10.1038/s41592-019-0686-2}.
\bibitem{pandas} The pandas development team \flqq pandas: powerful Python data analysis toolkit\frqq. \href{https://pandas.pydata.org/docs/pandas.pdf}{pandas.pydata.org/docs/pandas.pdf}.
\bibitem{numpy} Travis E. Oliphant. \flqq A guide to NumPy\frqq. USA: Trelgol Publishing, 2006. \href{https://numpy.org/doc/stable/}{numpy.org/doc/stable}.
\bibitem{plot} Hunter, J. D. \flqq Matplotlib: A 2D graphics environment\frqq. Computing in Science \& Engineering vol. 9, no. 3, pp. 90-95, 2007. \href{https://matplotlib.org/citing.html}{matplotlib.org/citing.html}.
\bibitem{imp} Официальный сайт документации Implicit: \href{https://implicit.readthedocs.io/en/latest/quickstart.html}{implicit.readthedocs.io/en/latest/quickstart.html}.
\bibitem{bib8} Steffen Rendle, Christoph Freudenthaler, Zeno Gantner, Lars Schmidt-Thieme \flqq BPR: Bayesian Personalized Ranking from Implicit Feedback\frqq. 	Appears in Proceedings of the Twenty-Fifth Conference on Uncertainty in Artificial Intelligence (UAI2009), \href{https://arxiv.org/abs/1205.2618}{arxiv.org/abs/1205.2618}.
\bibitem{voc3} F. Maxwell Harper and Joseph A. Konstan \flqq ACM Transactions on Interactive Intelligent Systems\frqq. ACM Trans. Interact. Intell. Syst. 5, 4, Article 19, 2015, \href{https://doi.org/10.1145/2827872}{doi.org/10.1145/2827872}.
\end{thebibliography}
\end{document}